SeedLing: Building and using a seed corpus \\ for the Human Language Project

### 2014-04-28 docs/computEL-final/cluster.tex
Formatting of links.

Language classification can be carried out in various ways. Two common approaches are genealogical classification, mapping languages onto family trees according to their historical relatedness \cite{swadesh1952,starostin2010}; and typological classification, grouping languages according to linguistic features \cite{georgi2010wals,daume2009}. Both of these approaches require linguistic analysis. By contrast, we use surface features (character n-gram and word unigram frequencies) extracted from SeedLing, and apply an off-the-shelf hierarchical clustering algorithm.\footnote{\url{http://www.scipy.org/}} Specifically, each language is represented as a vector of frequencies of character bigrams, character trigrams, and word unigrams. Each of these three components is normalized to unit length.

>>>>

Language classification can be carried out in various ways. Two common approaches are genealogical classification, mapping languages onto family trees according to their historical relatedness \cite{swadesh1952,starostin2010}; and typological classification, grouping languages according to linguistic features \cite{georgi2010wals,daume2009}. Both of these approaches require linguistic analysis. By contrast, we use surface features (character n-gram and word unigram frequencies) extracted from SeedLing, and apply an off-the-shelf hierarchical clustering algorithm.\footnote{\url{http://www.scipy.org}} Specifically, each language is represented as a vector of frequencies of character bigrams, character trigrams, and word unigrams. Each of these three components is normalized to unit length.

### 2014-04-28 docs/computEL-final/concl.tex
Formatting of links.

SeedLing (and the API) is currently available via a GitHub repository.\footnote{https://github.com/alvations/SeedLing} We have yet to fully address questions of long-term access, and we welcome ideas or collaborations along these lines.

>>>>

SeedLing (and the API) is currently available via a GitHub repository.\footnote{\url{https://github.com/alvations/SeedLing}} We have yet to fully address questions of long-term access, and we welcome ideas or collaborations along these lines.
